Dirac neutrino mass generation from Majorana messenger

### 2019-09-14 draft.tex
Updates from Overleaf

The most general Lagrangian contains the following Yukawa and scalar interactions:

@@

In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ and $\phi$ denote the new chiral fermions and new scalars respectively, and $q_{F,\,\phi}$ their $X$ charges. In the second row

@@

    \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \\
    &+  \lambda_{1} (H^{\dagger} H ) (S^{*} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{*} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
    &+ \lambda_{4} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{5} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\

@@

\section{Beyond the minimal model: cosmological constraints}
\label{sec:CosmoConstraints}
A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM. The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.

>>>>

The most general Lagrangian contains the following gauge, Yukawa and scalar interactions:

@@

In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges. In the second row

@@

    \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \nonumber\\
    &+  \lambda_{1} (H^{\dagger} H ) (S^{*} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{*} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\nonumber\\
    &+ \lambda_{4} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{5} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \nonumber\\

@@

\section{Beyond the minimal model: cosmological constraints}
\label{sec:CosmoConstraints}
\ref{eq:LagY}
It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{eff}.

A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM. The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
